Model LF

### 2022-10-13 Estimation.Rmd
Changes to the sensitivity analysis

```{r}
reg_prod=dynlm(TSDELTALOG(prod) ~ 1 + L(TSDELTALOG(prod),2:3) +  L(TSDELTA(s_h),c(1:2,4))  + L(log(prod),1) + L(s_h,1)+ L(log(mean_dp_regul),1) + L(log(mean_dp_regul),1))

>>>>

```{r}
reg_prod=dynlm(TSDELTALOG(prod) ~ 1 + L(TSDELTALOG(prod),2:3)  + L(log(prod),1) + L(s_h,1)+ L(log(mean_dp_regul),1) + L(log(mean_dp_regul),1) + d_2007q4)

### 2022-10-13 max_dp endogen stød.Rmd
commit
Changes to the sensitivity analysis

@@

COMMENT> 
BEHAVIORAL> prod_shock
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(prod_shock) = pr_0 + pr_1* TSDELTALOG(TSLAG(prod_shock,2)) + pr_2* TSDELTALOG(TSLAG(prod_shock,3)) + pr_3* TSDELTA(TSLAG(s_h,1))+  pr_4* TSDELTA(TSLAG(s_h,2)) + pr_5* TSDELTA(TSLAG(s_h,3)) + pr_6* TSDELTA(TSLAG(s_h,4))  + pr_8* LOG(TSLAG(dp_person,1)) + pr_9* TSLAG(s_h,1) + pr_10* LOG(TSLAG(prod_shock,1)) 
COEFF> pr_0 pr_1 pr_2 pr_3 pr_4 pr_5 pr_6 pr_8 pr_9 pr_10
STORE> coe(22)

COMMENT> 
BEHAVIORAL> prod_shock_sens
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(prod_shock_sens) = prs_0 + prs_1* TSDELTALOG(TSLAG(prod_shock_sens,2)) + prs_2* TSDELTALOG(TSLAG(prod_shock_sens,3)) + prs_3* TSDELTA(TSLAG(s_h,1))+  prs_4* TSDELTA(TSLAG(s_h,2)) + prs_5* TSDELTA(TSLAG(s_h,3)) + prs_6* TSDELTA(TSLAG(s_h,4))  + prs_8* LOG(TSLAG(dp_person,1)) + prs_9* TSLAG(s_h,1) + prs_10* LOG(TSLAG(prod_shock_sens,1)) 
RESTRICT> prs_8 = 0.1
COEFF> prs_0 prs_1 prs_2 prs_3 prs_4 prs_5 prs_6 prs_8 prs_9 prs_10
STORE> coe(24)

@@

  shock_1_model  = TIMESERIES(c(shock_1_model ),   
                           START=c(2005,2),FREQ=4),
  shock_2_model  = TIMESERIES(c(shock_2_model ),   
                           START=c(2005,2),FREQ=4),
  shock_3_model  = TIMESERIES(c(shock_3_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
   pf_shock = TIMESERIES(c(pf_shock),   
                        START=c(2005,2),FREQ=4),
  g_shock = TIMESERIES(c(g_shock),   
                        START=c(2005,2),FREQ=4),
  pm_ds_shock = TIMESERIES(c(pm_ds_shock),   
                        START=c(2005,2),FREQ=4),
  iloan_shock = TIMESERIES(c(iloan_shock),   
                        START=c(2005,2),FREQ=4),
  idep_shock = TIMESERIES(c(idep_shock),   
                        START=c(2005,2),FREQ=4),
   ibd_shock = TIMESERIES(c(ibd_shock),   
                        START=c(2005,2),FREQ=4),
  iboa_shock = TIMESERIES(c(iboa_shock),   
                        START=c(2005,2),FREQ=4),
   tax_rate1_shock = TIMESERIES(c(tax_rate1_shock),   
                        START=c(2005,2),FREQ=4),
  wage_gap = TIMESERIES(c(wage_gap),   
                        START=c(2006,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
  wage_ds_tt = TIMESERIES(c(wage_ds_tt),   
                        START=c(2006,1),FREQ=4),
   max_gap = TIMESERIES(c(max_gap),   
                        START=c(2005,2),FREQ=4),
   kont_h_ratio = TIMESERIES(c(kont_h_dp_person),   
                        START=c(2005,2),FREQ=4),
     kont_h = TIMESERIES(c(kont_h),   
                        START=c(2005,2),FREQ=4),
    prod_shock = TIMESERIES(c(prod),   
                        START=c(2005,2),FREQ=4),
   prod_shock = TIMESERIES(c(prod),   
                        START=c(2005,2),FREQ=4)
)
```

@@

S_modelData$sens3_low = sens3_low

@@

@@

nl_g_bs2 = Shock_bs2$simulation$nl_g

@@

```{r}
shock_prod_model_shock=shock_prod_model %>% window(start= c(2016,3))
```

@@

 shock_prod_model = TIMESERIES(shock_prod_model_shock+1 ,START=c(2016,3),  FREQ='Q')

@@

nl_g_bs3 = Shock_bs3$simulation$nl_g
inflation_bs3 = Shock_bs3$simulation$inflation

yd_hk_ds_bs3 = Shock_bs3$simulation$yd_hk_ds
wage_gap1_bs3 = Shock_bs3$simulation$wage_gap1
wage_gap_bs3 = Shock_bs3$simulation$wage_gap
prod_bs3 = Shock_bs3$simulation$prod
```

```{r}
plot(prod_bs3, col= "green"); lines(prod, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()
```

@@

@@

plot(wage_ds_t_02, col= "red"); lines(wage_ds_t_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

@@

@@

@@

  shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_prod_model = TIMESERIES(shock_prod_model_shock+1 ,START=c(2016,3),  FREQ='Q')

@@

```{r}
plot((ur_ds_03-ur_ds_bs3), col= "red")
```

@@

@@

@@

```{r}
###Gengivelse af stød til model
max_dp_sb_low = sens_1_base_low$simulation$max_dp
wage_sb_low = sens_1_base_low$simulation$wage
komp_r_sb_low = sens_1_base_low$simulation$komp_r
part_sb_low = sens_1_base_low$simulation$part
yk_ds_sb_low = sens_1_base_low$simulation$yk_ds
pc_ds_sb_low = sens_1_base_low$simulation$pc_ds
emp_sb_low = sens_1_base_low$simulation$emp
dp_person_sb_low = sens_1_base_low$simulation$dp_person

@@

```{r}
###Gengivelse af stød til model
max_dp_s1_low = sens_1_S1_low$simulation$max_dp
wage_s1_low = sens_1_S1_low$simulation$wage
komp_r_s1_low = sens_1_S1_low$simulation$komp_r
part_s1_low = sens_1_S1_low$simulation$part
yk_ds_s1_low = sens_1_S1_low$simulation$yk_ds
pc_ds_s1_low = sens_1_S1_low$simulation$pc_ds
emp_s1_low = sens_1_S1_low$simulation$emp
dp_person_s1_low = sens_1_S1_low$simulation$dp_person
```

@@

@@

```{r}
###Gengivelse af stød til model
max_dp_sb_up = sens_1_base_up$simulation$max_dp
wage_sb_up = sens_1_base_up$simulation$wage
komp_r_sb_up = sens_1_base_up$simulation$komp_r
part_sb_up = sens_1_base_up$simulation$part
yk_ds_sb_up = sens_1_base_up$simulation$yk_ds
pc_ds_sb_up = sens_1_base_up$simulation$pc_ds
emp_sb_up = sens_1_base_up$simulation$emp
dp_person_sb_up = sens_1_base_up$simulation$dp_person

@@

```{r}
###Gengivelse af stød til model
max_dp_s1_up = sens_1_S1_up$simulation$max_dp
wage_s1_up = sens_1_S1_up$simulation$wage
komp_r_s1_up = sens_1_S1_up$simulation$komp_r
part_s1_up = sens_1_S1_up$simulation$part
yk_ds_s1_up = sens_1_S1_up$simulation$yk_ds
pc_ds_s1_up = sens_1_S1_up$simulation$pc_ds
emp_s1_up = sens_1_S1_up$simulation$emp
dp_person_s1_up = sens_1_S1_up$simulation$dp_person
```

```{r}
plot((komp_r_s1_up/komp_r_sb_up), col= "red", main= "Compensation rate");
lines((komp_r_01/komp_r_00), col="black");
legend("top", legend=c("Estimate 0.85",
                       "Estimate 0.95"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

@@

@@

```{r}
###Gengivelse af stød til model
max_dp_sbs2_low = sens_2_bs_low$simulation$max_dp
wage_sbs2_low = sens_2_bs_low$simulation$wage
komp_r_sbs2_low = sens_2_bs_low$simulation$komp_r
part_sbs2_low = sens_2_bs_low$simulation$part
yk_ds_sbs2_low = sens_2_bs_low$simulation$yk_ds
pc_ds_sbs2_low = sens_2_bs_low$simulation$pc_ds
wage_ds_t_sbs2_low = sens_2_bs_low$simulation$wage_ds_t
pc_ds_sbs2_low = sens_2_bs_low$simulation$pc_ds
max_gap_sbs2_low = sens_2_bs_low$simulation$max_gap
wage_gap1_sbs2_low = sens_2_bs_low$simulation$wage_gap1
inflation_sbs2_low = sens_2_bs_low$simulation$inflation
wage_ds_sbs2_low = sens_2_bs_low$simulation$wage_ds

@@

```{r}
###Gengivelse af stød til model
max_dp_s2_low = sens_2_S1_low$simulation$max_dp
wage_s2_low = sens_2_S1_low$simulation$wage
komp_r_s2_low = sens_2_S1_low$simulation$komp_r
part_s2_low = sens_2_S1_low$simulation$part
yk_ds_s2_low = sens_2_S1_low$simulation$yk_ds
pc_ds_s2_low = sens_2_S1_low$simulation$pc_ds
wage_ds_t_s2_low = sens_2_S1_low$simulation$wage_ds_t
pc_ds_s2_low = sens_2_S1_low$simulation$pc_ds
max_gap_s2_low = sens_2_S1_low$simulation$max_gap
wage_ds_s2_low = sens_2_S1_low$simulation$wage_ds
wage_gap1_s2_low = sens_2_S1_low$simulation$wage_gap1
wage_gap_s2_low = sens_2_S1_low$simulation$wage_gap

inflation_s2_low = sens_2_S1_low$simulation$inflation
```

```{r}
plot((wage_ds_t_s2_low/wage_ds_t_sbs2_low), col= "red", ylim= c(0.9, 1.1));
lines((wage_ds_t_02/wage_ds_t_bs2), col="black");
legend("top", legend=c("wage_gap limit 38%",
                       "Wage_gap limit 40%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

@@

@@

```{r}
###Gengivelse af stød til model
max_dp_sbs2_up = sens_2_bs_up$simulation$max_dp
wage_sbs2_up = sens_2_bs_up$simulation$wage
komp_r_sbs2_up = sens_2_bs_up$simulation$komp_r
part_sbs2_up = sens_2_bs_up$simulation$part
yk_ds_sbs2_up = sens_2_bs_up$simulation$yk_ds
pc_ds_sbs2_up = sens_2_bs_up$simulation$pc_ds
wage_ds_t_sbs2_up = sens_2_bs_up$simulation$wage_ds_t
pc_ds_sbs2_up = sens_2_bs_up$simulation$pc_ds
max_gap_sbs2_up = sens_2_bs_up$simulation$max_gap
wage_gap1_sbs2_up = sens_2_bs_up$simulation$wage_gap1
inflation_sbs2_up = sens_2_bs_up$simulation$inflation
wage_ds_sbs2_up = sens_2_bs_up$simulation$wage_ds

@@

```{r}
###Gengivelse af stød til model
max_dp_s2_up = sens_2_S1_up$simulation$max_dp
wage_s2_up = sens_2_S1_up$simulation$wage
komp_r_s2_up = sens_2_S1_up$simulation$komp_r
part_s2_up = sens_2_S1_up$simulation$part
yk_ds_s2_up = sens_2_S1_up$simulation$yk_ds
pc_ds_s2_up = sens_2_S1_up$simulation$pc_ds
wage_ds_t_s2_up = sens_2_S1_up$simulation$wage_ds_t
pc_ds_s2_up = sens_2_S1_up$simulation$pc_ds
max_gap_s2_up = sens_2_S1_up$simulation$max_gap
wage_ds_s2_up = sens_2_S1_up$simulation$wage_ds
wage_gap1_s2_up = sens_2_S1_up$simulation$wage_gap1
wage_gap_s2_up = sens_2_S1_up$simulation$wage_gap

inflation_s2_up = sens_2_S1_up$simulation$inflation
```

```{r}
plot((wage_ds_t_s2_up/wage_ds_t_sbs2_up), col= "red", ylim= c(0.9, 1.1));
lines((wage_ds_t_02/wage_ds_t_bs2), col="black");
legend("top", legend=c("No suppression",
                       "Wage growth"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((inflation_s2_up-inflation_sbs2_up), col= "red", ylim= c(-0.0004, 0.0035));
lines((inflation_02-inflation_00), col="black");
legend("top", legend=c("No suppression",
                       "Wage growth"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((wage_ds_s2_up/wage_ds_sbs2_up), col= "red", ylim= c(0.995, 1.02));
lines((wage_ds_02/wage_ds_00), col="black");
legend("top", legend=c("No suppression",
                       "Wage growth"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

@@

prod_sbs3_low = sens_3_bs_low$simulation$prod
```

@@

```{r}
###Gengivelse af stød til model
max_dp_s3_low = sens_3_S1_low$simulation$max_dp
wage_s3_low = sens_3_S1_low$simulation$wage
komp_r_s3_low = sens_3_S1_low$simulation$komp_r
part_s3_low = sens_3_S1_low$simulation$part
yk_ds_s3_low = sens_3_S1_low$simulation$yk_ds
pc_ds_s3_low = sens_3_S1_low$simulation$pc_ds
wage_ds_t_s3_low = sens_3_S1_low$simulation$wage_ds_t
pc_ds_s3_low = sens_3_S1_low$simulation$pc_ds
max_gap_s3_low = sens_3_S1_low$simulation$max_gap
wage_ds_s3_low = sens_3_S1_low$simulation$wage_ds
wage_gap1_s3_low = sens_3_S1_low$simulation$wage_gap1
wage_gap_s3_low = sens_3_S1_low$simulation$wage_gap

inflation_s3_low = sens_3_S1_low$simulation$inflation
emp_s3_low = sens_3_S1_low$simulation$emp

@@

```{r}
plot((prod_s3_low/prod_sbs3_low), col= "red", ylim= c(0.9, 1.1), main= "Productivity");
lines((prod_03/prod_bs3), col="black");
legend("top", legend=c("Estimate set to 0.1",
                       "Estimate is 0.25"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((inflation_s3_low-inflation_sbs3_low), col= "red", ylim= c(-0.0004, 0.0035));
lines((inflation_03-inflation_bs3), col="black");
legend("top", legend=c("Estimate set to 0.1",
                       "Estimate is 0.25"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

@@

>>>>

d_2007q4=create_dummy_ts(start_basic = c(2005, 2), end_basic=c(2020,1),
 dummy_start=c(2007,4), dummy_end = c(2007,4),
 basic_value = 0, dummy_value = 1, frequency = 4)

@@

COMMENT> 
BEHAVIORAL> prod_shock
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(prod_shock) = pr_0 + pr_1* TSDELTALOG(TSLAG(prod_shock,2)) + pr_2* TSDELTALOG(TSLAG(prod_shock,3))  + pr_8* LOG(TSLAG(dp_person,1)) + pr_9* TSLAG(s_h,1) + pr_10* LOG(TSLAG(prod_shock,1)) + pr_11 * d_2007q4 
COEFF> pr_0 pr_1 pr_2 pr_8 pr_9 pr_10 pr_11
STORE> coe(22)

COMMENT> 
BEHAVIORAL> prod_shock_sens
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(prod_shock_sens) = prs_0 + prs_1* TSDELTALOG(TSLAG(prod_shock,2)) + prs_2* TSDELTALOG(TSLAG(prod_shock,3))  + prs_8* LOG(TSLAG(dp_person,1)) + prs_9* TSLAG(s_h,1) + prs_10* LOG(TSLAG(prod_shock,1)) + prs_11 * d_2007q4
RESTRICT> prs_8 = 0.1
COEFF> prs_0 prs_1 prs_2 prs_8 prs_9 prs_10 prs_11
STORE> coe(24)

@@

  shock_1_model  = TIMESERIES(c(shock_1_model ),   
                           START=c(2005,2),FREQ=4),
  shock_2_model  = TIMESERIES(c(shock_2_model ),   
                           START=c(2005,2),FREQ=4),
  shock_3_model  = TIMESERIES(c(shock_3_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
   pf_shock = TIMESERIES(c(pf_shock),   
                        START=c(2005,2),FREQ=4),
  g_shock = TIMESERIES(c(g_shock),   
                        START=c(2005,2),FREQ=4),
  pm_ds_shock = TIMESERIES(c(pm_ds_shock),   
                        START=c(2005,2),FREQ=4),
  iloan_shock = TIMESERIES(c(iloan_shock),   
                        START=c(2005,2),FREQ=4),
  idep_shock = TIMESERIES(c(idep_shock),   
                        START=c(2005,2),FREQ=4),
   ibd_shock = TIMESERIES(c(ibd_shock),   
                        START=c(2005,2),FREQ=4),
  iboa_shock = TIMESERIES(c(iboa_shock),   
                        START=c(2005,2),FREQ=4),
   tax_rate1_shock = TIMESERIES(c(tax_rate1_shock),   
                        START=c(2005,2),FREQ=4),
  wage_gap = TIMESERIES(c(wage_gap),   
                        START=c(2006,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
  wage_ds_tt = TIMESERIES(c(wage_ds_tt),   
                        START=c(2006,1),FREQ=4),
   max_gap = TIMESERIES(c(max_gap),   
                        START=c(2005,2),FREQ=4),
   kont_h_ratio = TIMESERIES(c(kont_h_dp_person),   
                        START=c(2005,2),FREQ=4),
     kont_h = TIMESERIES(c(kont_h),   
                        START=c(2005,2),FREQ=4),
    prod_shock = TIMESERIES(c(prod),   
                        START=c(2005,2),FREQ=4),
   prod_shock = TIMESERIES(c(prod),   
                        START=c(2005,2),FREQ=4),
  d_2007q4 = TIMESERIES(c(d_2007q4),   
                        START=c(2005,2),FREQ=4)
)
```

@@

S_modelData$d_2007q4 = d_2007q4

@@

plot(ur_ds_00, col= "green"); lines(ur_ds, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

@@

nl_g_bs2 = Shock_bs2$simulation$nl_g
inflation_bs2 = Shock_bs2$simulation$inflation

@@

```{r}
shock_prod_model_shock=shock_prod_model %>% window(start= c(2006,3))
```

@@

 shock_prod_model = TIMESERIES(shock_prod_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

nl_g_bs3 = Shock_bs3$simulation$nl_g

s_h_bs3 = Shock_bs3$simulation$s_h
inflation_bs3 = Shock_bs3$simulation$inflation

yd_hk_ds_bs3 = Shock_bs3$simulation$yd_hk_ds
wage_gap1_bs3 = Shock_bs3$simulation$wage_gap1
wage_gap_bs3 = Shock_bs3$simulation$wage_gap
prod_bs3 = Shock_bs3$simulation$prod

ur_bs3 = Shock_bs3$simulation$ur
```

```{r}
plot(prod_bs3, col= "green"); lines(prod, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(ur_ds_bs3, col= "green"); lines(ur_ds, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(ur_bs3, col= "green"); lines(ur, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(emp_bs3, col= "green"); lines(emp, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

plot(yk_ds_bs3, col= "green"); lines(yk_ds, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()
```

@@

```{r}
plot((nl_g_01-nl_g_00), col= "red")
```

@@

plot(wage_ds_t_02, col= "red"); lines(wage_ds_t_bs2, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

@@

plot(wage_ds_02, col= "red"); lines(wage_ds_bs2, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

@@

```{r}
plot((nl_g_02-nl_g_bs2), col= "red")
```

@@

  shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_prod_model = TIMESERIES(shock_prod_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

```{r}
plot((nl_g_03-nl_g_bs3), col= "red")
```

@@

```{r}
plot((nl_g_04-nl_g_bs4), col= "red")
```

@@

```{r}
plot((nl_g_05-nl_g_bs56), col= "red")
```

@@

```{r}
###Gengivelse af stød til model
max_dp_sb_low = sens_1_base_low$simulation$max_dp
wage_sb_low = sens_1_base_low$simulation$wage
komp_r_sb_low = sens_1_base_low$simulation$komp_r
part_sb_low = sens_1_base_low$simulation$part
yk_ds_sb_low = sens_1_base_low$simulation$yk_ds
pc_ds_sb_low = sens_1_base_low$simulation$pc_ds
emp_sb_low = sens_1_base_low$simulation$emp
dp_person_sb_low = sens_1_base_low$simulation$dp_person
nl_g_sb_low = sens_1_base_low$simulation$nl_g
```

@@

```{r}
###Gengivelse af stød til model
max_dp_s1_low = sens_1_S1_low$simulation$max_dp
wage_s1_low = sens_1_S1_low$simulation$wage
komp_r_s1_low = sens_1_S1_low$simulation$komp_r
part_s1_low = sens_1_S1_low$simulation$part
yk_ds_s1_low = sens_1_S1_low$simulation$yk_ds
pc_ds_s1_low = sens_1_S1_low$simulation$pc_ds
emp_s1_low = sens_1_S1_low$simulation$emp
dp_person_s1_low = sens_1_S1_low$simulation$dp_person
nl_g_s1_low = sens_1_S1_low$simulation$nl_g
```

@@

```{r}
plot((emp_s1_low-emp_sb_low)*1000, col= "red")
```

```{r}
plot((nl_g_s1_low-nl_g_sb_low), col= "red")
```

@@

```{r}
###Gengivelse af stød til model
max_dp_sb_up = sens_1_base_up$simulation$max_dp
wage_sb_up = sens_1_base_up$simulation$wage
komp_r_sb_up = sens_1_base_up$simulation$komp_r
part_sb_up = sens_1_base_up$simulation$part
yk_ds_sb_up = sens_1_base_up$simulation$yk_ds
pc_ds_sb_up = sens_1_base_up$simulation$pc_ds
emp_sb_up = sens_1_base_up$simulation$emp
dp_person_sb_up = sens_1_base_up$simulation$dp_person
nl_g_sb_up = sens_1_base_up$simulation$nl_g
```

@@

```{r}
###Gengivelse af stød til model
max_dp_s1_up = sens_1_S1_up$simulation$max_dp
wage_s1_up = sens_1_S1_up$simulation$wage
komp_r_s1_up = sens_1_S1_up$simulation$komp_r
part_s1_up = sens_1_S1_up$simulation$part
yk_ds_s1_up = sens_1_S1_up$simulation$yk_ds
pc_ds_s1_up = sens_1_S1_up$simulation$pc_ds
emp_s1_up = sens_1_S1_up$simulation$emp
dp_person_s1_up = sens_1_S1_up$simulation$dp_person
nl_g_s1_up = sens_1_S1_up$simulation$nl_g
```

```{r}
plot((komp_r_s1_up/komp_r_sb_up), col= "red", main= "Compensation rate");
lines((komp_r_01/komp_r_00), col="black");
legend("top", legend=c("Estimate 0.99",
                       "Estimate 0.95"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

@@

```{r}
plot((emp_s1_up-emp_sb_up)*1000, col= "red")
```

```{r}
plot((nl_g_s1_up-nl_g_sb_up), col= "red")
```

@@

```{r}
###Gengivelse af stød til model
max_dp_sbs2_low = sens_2_bs_low$simulation$max_dp
wage_sbs2_low = sens_2_bs_low$simulation$wage
komp_r_sbs2_low = sens_2_bs_low$simulation$komp_r
part_sbs2_low = sens_2_bs_low$simulation$part
yk_ds_sbs2_low = sens_2_bs_low$simulation$yk_ds
pc_ds_sbs2_low = sens_2_bs_low$simulation$pc_ds
wage_ds_t_sbs2_low = sens_2_bs_low$simulation$wage_ds_t
pc_ds_sbs2_low = sens_2_bs_low$simulation$pc_ds
max_gap_sbs2_low = sens_2_bs_low$simulation$max_gap
wage_gap1_sbs2_low = sens_2_bs_low$simulation$wage_gap1
inflation_sbs2_low = sens_2_bs_low$simulation$inflation
wage_ds_sbs2_low = sens_2_bs_low$simulation$wage_ds
emp_sbs2_low = sens_2_bs_low$simulation$emp
nl_g_sbs2_low = sens_2_bs_low$simulation$nl_g
```

@@

```{r}
###Gengivelse af stød til model
max_dp_s2_low = sens_2_S1_low$simulation$max_dp
wage_s2_low = sens_2_S1_low$simulation$wage
komp_r_s2_low = sens_2_S1_low$simulation$komp_r
emp_s2_low = sens_2_S1_low$simulation$emp
yk_ds_s2_low = sens_2_S1_low$simulation$yk_ds
pc_ds_s2_low = sens_2_S1_low$simulation$pc_ds
wage_ds_t_s2_low = sens_2_S1_low$simulation$wage_ds_t
pc_ds_s2_low = sens_2_S1_low$simulation$pc_ds
max_gap_s2_low = sens_2_S1_low$simulation$max_gap
wage_ds_s2_low = sens_2_S1_low$simulation$wage_ds
wage_gap1_s2_low = sens_2_S1_low$simulation$wage_gap1
wage_gap_s2_low = sens_2_S1_low$simulation$wage_gap
nl_g_s2_low = sens_2_S1_low$simulation$nl_g
inflation_s2_low = sens_2_S1_low$simulation$inflation
```

```{r}
plot((wage_ds_t_s2_low/wage_ds_t_sbs2_low), col= "red", ylim= c(0.98, 1.02));
lines((wage_ds_t_02/wage_ds_t_bs2), col="black");
legend("top", legend=c("wage_gap limit 38%",
                       "Wage_gap limit 40%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

@@

```{r}
plot((emp_s2_low-emp_sbs2_low)*1000, col= "red")
```

Effect on government net lending:

```{r}
plot((nl_g_s2_low-nl_g_sbs2_low), col= "red")
```

@@

```{r}
###Gengivelse af stød til model
max_dp_sbs2_up = sens_2_bs_up$simulation$max_dp
wage_sbs2_up = sens_2_bs_up$simulation$wage
komp_r_sbs2_up = sens_2_bs_up$simulation$komp_r
part_sbs2_up = sens_2_bs_up$simulation$part
yk_ds_sbs2_up = sens_2_bs_up$simulation$yk_ds
pc_ds_sbs2_up = sens_2_bs_up$simulation$pc_ds
wage_ds_t_sbs2_up = sens_2_bs_up$simulation$wage_ds_t
pc_ds_sbs2_up = sens_2_bs_up$simulation$pc_ds
max_gap_sbs2_up = sens_2_bs_up$simulation$max_gap
wage_gap1_sbs2_up = sens_2_bs_up$simulation$wage_gap1
inflation_sbs2_up = sens_2_bs_up$simulation$inflation
wage_ds_sbs2_up = sens_2_bs_up$simulation$wage_ds
emp_sbs2_up = sens_2_bs_up$simulation$emp
u_ds_sbs2_up = sens_2_bs_up$simulation$u_ds
nl_g_sbs2_up = sens_2_bs_up$simulation$nl_g
```

@@

```{r}
###Gengivelse af stød til model
max_dp_s2_up = sens_2_S1_up$simulation$max_dp
wage_s2_up = sens_2_S1_up$simulation$wage
komp_r_s2_up = sens_2_S1_up$simulation$komp_r
emp_s2_up = sens_2_S1_up$simulation$emp
yk_ds_s2_up = sens_2_S1_up$simulation$yk_ds
pc_ds_s2_up = sens_2_S1_up$simulation$pc_ds
wage_ds_t_s2_up = sens_2_S1_up$simulation$wage_ds_t
pc_ds_s2_up = sens_2_S1_up$simulation$pc_ds
max_gap_s2_up = sens_2_S1_up$simulation$max_gap
wage_ds_s2_up = sens_2_S1_up$simulation$wage_ds
wage_gap1_s2_up = sens_2_S1_up$simulation$wage_gap1
wage_gap_s2_up = sens_2_S1_up$simulation$wage_gap
u_ds_s2_up = sens_2_S1_up$simulation$u_ds
inflation_s2_up = sens_2_S1_up$simulation$inflation
nl_g_s2_up = sens_2_S1_up$simulation$nl_g
```

```{r}
plot((wage_ds_t_s2_up/wage_ds_t_sbs2_up), col= "red", ylim= c(0.95, 1.1), main= "Targeted Wage");
lines((wage_ds_t_02/wage_ds_t_bs2), col="black");
legend("top", legend=c("Wage-gap limit 42%",
                       "Wage-gap limit 40%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((inflation_s2_up-inflation_sbs2_up), col= "red", ylim= c(-0.0004, 0.0035), main= "Inflation");
lines((inflation_02-inflation_bs2), col="black");
legend("top", legend=c("Wage-gap limit 42%",
                       "Wage-gap limit 40%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((wage_ds_s2_up/wage_ds_sbs2_up), col= "red", ylim= c(0.995, 1.04), main= "Wage");
lines((wage_ds_02/wage_ds_bs2), col="black");
legend("top", legend=c("Wage-gap limit 42%",
                       "Wage-gap limit 40%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((u_ds_s2_up/u_ds_sbs2_up), col= "red", ylim= c(0.998, 1.005), main= "Capacity utilization");
lines((u_ds_02/u_ds_bs2), col="black");
legend("top", legend=c("Wage-gap limit 42%",
                       "Wage-gap limit 40%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((emp_s2_up-emp_sbs2_up)*1000, col= "red")
```

```{r}
plot((nl_g_s2_up-nl_g_sbs2_up), col= "red")
```

@@

nl_g_sbs3_low = sens_3_bs_low$simulation$nl_g
prod_sbs3_low = sens_3_bs_low$simulation$prod
```

@@

```{r}
max_dp_s3_low = sens_3_S1_low$simulation$max_dp
wage_s3_low = sens_3_S1_low$simulation$wage
komp_r_s3_low = sens_3_S1_low$simulation$komp_r
part_s3_low = sens_3_S1_low$simulation$part
yk_ds_s3_low = sens_3_S1_low$simulation$yk_ds
pc_ds_s3_low = sens_3_S1_low$simulation$pc_ds
wage_ds_t_s3_low = sens_3_S1_low$simulation$wage_ds_t
pc_ds_s3_low = sens_3_S1_low$simulation$pc_ds
max_gap_s3_low = sens_3_S1_low$simulation$max_gap
wage_ds_s3_low = sens_3_S1_low$simulation$wage_ds
wage_gap1_s3_low = sens_3_S1_low$simulation$wage_gap1
wage_gap_s3_low = sens_3_S1_low$simulation$wage_gap

inflation_s3_low = sens_3_S1_low$simulation$inflation
emp_s3_low = sens_3_S1_low$simulation$emp
nl_g_s3_low = sens_3_S1_low$simulation$nl_g

@@

```{r}
plot((prod_s3_low/prod_sbs3_low), col= "red", ylim= c(0.9, 1.1), main= "Productivity");
lines((prod_03/prod_bs3), col="black");
legend("top", legend=c("Estimate set to 0.1",
                       "Estimate is 0.2"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((inflation_s3_low-inflation_sbs3_low), col= "red", ylim= c(-0.0004, 0.0035));
lines((inflation_03-inflation_bs3), col="black");
legend("top", legend=c("Estimate set to 0.1",
                       "Estimate is 0.2"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

@@

```{r}
plot((nl_g_s3_low-nl_g_sbs3_low), col= "red")
```
